\documentclass[
    a4paper,%
    12pt,%
    oneside, %
    openany, %
]{report}

\input{tex/preamble}


\begin{document}
\baselineskip24pt

\thispagestyle{empty}
\thispagestyle{empty}
%\maketitle
%\begin{center}
%	\date{DECEMBER, 2021.}
%\end{center}

\addcontentsline{toc}{chapter}{Title Page}
\begin{center}
    \begin{LARGE}
        \textsc{Topology of robot motion planning algorithms}
    \end{LARGE}
    \\[3em]
    {BY}\\[3em]
    \begin{large}
        \textsc{Fawole Abdulrasheed Bolaji}\\
        \textsc{Matric Number: 207256}\\[4em]
    \end{large}
    A PROJECT SUBMITTED TO THE DEPARTMENT OF MATHEMATICS, FACULTY OF SCIENCE, UNIVERSITY OF IBADAN, IBADAN, NIGERIA IN PARTIAL FULFILMENT OF THE REQUIREMENTS FOR THE AWARD OF THE BACHELOR OF SCIENCE DEGREE IN MATHEMATICS\\[5em]
        
        JULY,\;2023
\end{center}

\newpage


\chapter*{Certification}
\addcontentsline{toc}{chapter}{Certification}

\renewcommand{\thepage}{\roman{page}}
I certify that this project work was carried out by \textsc{Fawole Abdulrasheed Bolaji} with matriculation number \textbf{207256}, of the Department of Mathematics, Faculty of Science, University of Ibadan, under the supervision of \textbf{Professor Deborah O.A Ajayi}.
\vspace*{3cm}
\begin{center}
    \line(1,0){350}\\
    (Supervisor)\\
    \vspace*{-0.25cm}
    \textbf{Professor Deborah O.A. Ajayi}
    \\
    \vspace*{-0.25cm}
    Department of Mathematics,
    \\
    \vspace*{-0.25cm}
    University of Ibadan,
    \\
    \vspace*{-0.25cm}
    Ibadan, Nigeria.

\end{center}
\newpage


\chapter*{Dedication}
\addcontentsline{toc}{chapter}{Dedication}
This project is dedicated to Almighty ALLAH for His constant grace and mercy over my life and for seeing me through the successful completion of my B.Sc. programme, to my parents and to my late grandpa, Pa Abdul-Lateef Adeleke Fawole.


\chapter*{Acknowledgement}
\addcontentsline{toc}{chapter}{Acknowledgement}
I give thanks to Almighty ALLAH for granting me the grace and the ability to conclude this B.Sc. programme.

First and foremost, I extend my deepest appreciation to my supervisor, Professor Deborah O.A. Ajayi, for her invaluable guidance, encouragement, and unwavering support throughout the project. Her expertise, patience, and constructive feedback have been instrumental in shaping the direction and quality of this work. I am grateful for the time and effort she invested, which has been pivotal in enhancing my understanding of the subject matter. May Almighty God Continue take you to greater heights in all your entire endeavours. 

I am equally grateful to all my lecturers, the academic pillars in Mathematics Department, whose unwavering dedication to education and pursuit of excellence have created a nurturing academic environment for me.

Furthermore, I am indebted to my friends and classmates who provided moral support and shared their insights and ideas during various stages of this project.

I would like to acknowledge the authors and researchers whose scholarly work served as a foundation for my study. Their contributions to the field have been inspiring and have provided me with valuable references and theoretical frameworks.

Lastly, I extend my heartfelt appreciation to my family for their unwavering love, encouragement, and support throughout my academic journey. Their belief in me and their constant motivation have been my driving force in overcoming challenges and striving for excellence.

In conclusion, this undergraduate final year project has been a fulfilling and rewarding experience, and I am grateful to everyone who has played a part in making it a reality. Each individual mentioned here has left an indelible mark on my academic and personal growth, and I am deeply thankful for their contributions.

Thank you all.



\newpage



% \maketitle
\pagenumbering{roman}
\tableofcontents
\listoffigures
\newpage
\pagenumbering{arabic}
\input{tex/ch1}
\input{tex/ch2}
\input{tex/ch3}
\input{tex/ch4}

\addcontentsline{toc}{chapter}{References}
\bibliographystyle{apalike}
\bibliography{references}





\end{document}